---
title: "Assignment_7"
description: |
  Community Detection (Marriages between characters in the Game of Thrones Novels)
author:
  - name: Walid Medani
    url: https://walidmedani.github.io/networks-blog/
date: 2022-03-24
output:
  distill::distill_article:
    self_contained: false
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(igraph)
library(tidyverse)
library(statnet)
```

```{r include=FALSE}
#First let's do some set up
  if("statnet"   %in% rownames(installed.packages()) == FALSE) {install.packages("statnet")}
  if("igraph"   %in% rownames(installed.packages()) == FALSE) {install.packages("igraph")}
  if("gsheet"   %in% rownames(installed.packages()) == FALSE) {install.packages("gsheet")}
  

  library(statnet)
  library(igraph)
  library(gsheet)
  library(gdata)

#First let's load the data
  ##data in edgelist format
  relationships<-gsheet2tbl("https://docs.google.com/spreadsheets/d/1THL4Q4NO4XdFtF2Lgk3lpGuPOffLIp2Nk6y3XgvHnGs/edit?usp=sharing")
  relationships$To<-ifelse(relationships$To=="Unknown",ifelse(relationships$From=="Frey", "North", relationships$From),relationships$To)

  ##also import family and color information to match
  family<-gsheet2tbl("https://docs.google.com/spreadsheets/d/19w8dij4snBSREMpDoGzHXGC4K6Su0D8j2SY1rPYFSLQ/edit?usp=sharing")
  
##all marriages
  marriages<-relationships%>%
  filter(Type!="Affair")%>%
  group_by(From,To)%>%
  summarise(weight=n())

#Lets create a igraph object
      network_igraph<-graph_from_edgelist(as.matrix(marriages[,1:2]), directed=FALSE)
      E(network_igraph)$weight<-marriages$weight
      gotmarr.mat<-as.matrix(as_adj(network_igraph, attr="weight"))
      
      #igraph won't correct for strange edgelist with some asymmetry
      #export to statnet to fix and then reimport
      gotmarr.stat <- network(gotmarr.mat,ignore.eval=FALSE, names.eval="weight",directed = FALSE, loops=TRUE )
      gotmarr.stat%v%"color"<-family$Color[match(gotmarr.stat%v%"name", family$Family)]
      gotmarr.stat%v%"region"<-family$Region[match(gotmarr.stat%v%"name", family$Family)]
      gotmarr.mat<-as.matrix.network(gotmarr.stat,attrname = "weight")
      
      #reimport to igraph
      gotmarr.ig<-intergraph::asIgraph(gotmarr.stat)
      V(gotmarr.ig)$name<-V(gotmarr.ig)$vertex.names
      
      #all partners
      partners<-relationships%>%
        filter(Type!="Engaged")%>%
      group_by(From,To)%>%
        summarise(weight=n())
      
      #Lets create a igraph object
      network_igraph<-graph_from_edgelist(as.matrix(partners[,1:2]), directed=FALSE)
      E(network_igraph)$weight<-partners$weight
      gotpart.mat<-as.matrix(as_adj(network_igraph,attr="weight"))
      
      #igraph won't correct for strange edgelist with some asymmetry
      #export to statnet to fix and then reimport
      gotpart.stat <- network(gotpart.mat,ignore.eval=FALSE, names.eval="weight", directed = FALSE, loops=TRUE)
      gotpart.stat%v%"color"<-family$Color[match(gotpart.stat%v%"name", family$Family)]
      gotpart.stat%v%"region"<-family$Region[match(gotpart.stat%v%"name", family$Family)]
      gotpart.mat<-as.matrix.network(gotpart.stat,attrname = "weight")
  
      #reimport to igraph
      gotpart.ig<-intergraph::asIgraph(gotpart.stat)
      V(gotpart.ig)$name<-V(gotpart.ig)$vertex.names
      
  #Let's remove unessesary objects
  rm(family)
  rm(marriages)
  rm(network_igraph)
  rm(partners)
  
  gotmarr.nodes<-data.frame(name=gotmarr.stat%v%"vertex.names",
        degree=sna::degree(gotmarr.stat,gmode="graph"),
        degree.wt=strength(gotmarr.ig),
        bonpow=sna::bonpow(gotmarr.stat),
        betweenness=sna::betweenness(gotmarr.stat, gmode="graph"),
        close=sna::closeness(gotmarr.stat, gmode="graph"),
        constraint=constraint(gotmarr.ig))
```

# Game of Thrones Marriages
```{r}
plot.igraph(gotmarr.ig, 
            vertex.label.cex=1)
```
# Network Size
```{r}
vcount(gotmarr.ig)
ecount(gotmarr.ig)
```
# Attributes
```{r}
is_bipartite(gotmarr.ig)
is_directed(gotmarr.ig)
is_weighted(gotmarr.ig)
vertex_attr_names(gotmarr.ig)
edge_attr_names(gotmarr.ig)
```

# Community Detection

## Fast and greedy
```{r}
#Run clustering algorithm: fast_greedy
got.fg<-cluster_fast_greedy(gotmarr.ig)
#Retrieve list of nodes in communities
igraph::groups(got.fg)
plot(got.fg,gotmarr.ig)
```
## Walktrap
```{r}
nodes.by.gp<-function(network.nodes, groupvar){
  network.nodes%>%
  select(-name)%>%
  group_by_(groupvar) %>%
  mutate(n=n())%>%
  summarise_all(mean, na.rm=TRUE)%>%
  as.matrix()%>%
  print(digits=2)
}


got.wt<-walktrap.community(gotmarr.ig)
igraph::groups(got.wt)
gotmarr.nodes$comm.wt<-got.wt$membership
nodes.by.gp(gotmarr.nodes,"comm.wt")
plot(got.wt,gotmarr.ig)
```

## Label Propagation
```{r}
got.lab<-walktrap.community(gotmarr.ig)
igraph::groups(got.lab)
gotmarr.nodes$comm.lab<-got.lab$membership
nodes.by.gp(gotmarr.nodes,"comm.lab")
plot(got.lab,gotmarr.ig)
```
## Edge betweeness
```{r warning=FALSE}
got.edge<-edge.betweenness.community(gotmarr.ig)
igraph::groups(got.edge)
gotmarr.nodes$comm.edge<-got.edge$membership
nodes.by.gp(gotmarr.nodes,"comm.edge")
plot(got.edge,gotmarr.ig)
```

## Eigenvector
```{r}
got.eigen<-leading.eigenvector.community(gotmarr.ig)
igraph::groups(got.eigen)
gotmarr.nodes$comm.eigen<-got.eigen$membership
nodes.by.gp(gotmarr.nodes,"comm.eigen")
plot(got.eigen,gotmarr.ig)
```

# Modularity Scores
```{r echo=FALSE}
mods<-c(fastgreedy=modularity(got.fg), walktrap=modularity(got.wt), label=modularity(got.lab), edge=modularity(got.edge), eigen=modularity(got.eigen))
mods
```

# Observations
For the GOT marriages data set, the fast/greedy, walktrap, and label propagation made the most sense in identifying communities. Fast and greedy was the most successful method due to it partitioning "Baratheon", "Reach", and "Tyrell" as a separate community from the northern kingdoms of "Tully" and "Arryn" where there was a weak or no relationship between the factions.

Edge betweeness failed to identify any communities within the dataset, whereas the Eigenvector failed to cluster some memberships such as the Reach being distinct from the Tyrell family (rulers of the region) and has strong marriage connections with the Baratheons.

