---
title: "Assignment_2"
description: |
  Network of militarized interstate disputes from 1870 to 2014. (https://correlatesofwar.org/data-sets/MIDs)
author:
  - name: Walid Medani
    url: https://walidmedani.github.io/networks-blog/
date: 2022-02-02
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r message=FALSE, warning=FALSE, include=FALSE}
library(igraph)
library(statnet)
library(tidyverse)
```

```{r include=FALSE}
#Read in network data
urlfile<-'https://raw.githubusercontent.com/walidmedani/networks-blog/main/MIDIP5.csv'
net_data<-read.csv(urlfile)


#This is an affiliation network, based on shared participation in conflicts#
mid_net_2<-graph.edgelist(as.matrix(net_data[,c("dispnum","stabb")]),directed=F)

#An easy way to collapse this is through matrix multiplication#
#First, get the full adjacency matrix#
mid_mat<-as.matrix(get.adjacency(mid_net_2))
dim(mid_mat) #Square matrix
row.names(mid_mat)[1:10] #Mix of countries and conflicts
colnames(mid_mat)[1:10] #Same in rows

#Next, isolate rows to conflicts and columns to states#
mid_mat<-mid_mat[which(row.names(mid_mat) %in% net_data$dispnum),
                 which(colnames(mid_mat) %in% net_data$stabb)]
dim(mid_mat) #Rectangular matrix - conflict x country
row.names(mid_mat)[1:10] #Conflicts in rows
colnames(mid_mat)[1:10] #Countries in columns

#Finally, multiply by the transposition of the network#
#This either gives us a 1-mode conflict network based on shared participants...#
conflict_mat<-mid_mat %*% t(mid_mat)
row.names(conflict_mat)[1:10] #Only conflicts
colnames(conflict_mat)[1:10] #in columns too

#... or the 1- mode state network, based on shared conflicts#
state_mat<-t(mid_mat) %*% mid_mat
row.names(state_mat)[1:10] #Only states
colnames(state_mat)[1:10] #in columns too
#Edges are number of conflicts in which any two countries both participated#
wardata<-graph.adjacency(state_mat,mode="undirected",weighted=T,diag = F)
```
# Network Graph
```{r}
plot(wardata,vertex.label=NA,vertex.size=3)
```

# Network Size
```{r}
vcount(wardata)
ecount(wardata)
```
# Attributes
```{r}
is_bipartite(wardata)
is_directed(wardata)
is_weighted(wardata)
vertex_attr_names(wardata)
edge_attr_names(wardata)
```
Network isn't bipartite nor directed however it is weighted.

# Dyad & Triad Census
```{r}
igraph::dyad.census(wardata)
igraph::triad_census(wardata)
sum(igraph::triad_census(wardata))

dyaddata <- data.frame(Mut = 1374, Asym = 0, Null = 10716)
triaddata <- data.frame(Triad0 = 449446, Triad1 = 144438, Triad2 = 13050, Triad3 = 13686, Triadsum = 620620)
tibble(dyaddata)
tibble(triaddata)
```


# Transivity
```{r}
transitivity(wardata, type="global")
transitivity(wardata, type="average")
```
Global transivity shows a proportion of .76 of completely connected triads within the network and the density of the ego network is .65.

# Geodesic & Component structure
```{r}
average.path.length(wardata,directed=F)
igraph::components(wardata)$no
igraph::components(wardata)$csize
```
There are 4 components with the first comprising of 150 members and the next 3 components having only 2 members each.

# Network density
```{r}
graph.density(wardata)
```
