---
title: "Assignment_8"
description: |
  Network Statistics (Marriages between characters in the Game of Thrones Novels).
author:
  - name: Walid Medani
    url: https://walidmedani.github.io/networks-blog/
date: 2022-04-06
output:
  distill::distill_article:
    self_contained: false
---

```{r warning=FALSE, include=FALSE}
library(igraph)
library(tidyverse)
library(statnet)
```

```{r include=FALSE}
#First let's do some set up
  if("statnet"   %in% rownames(installed.packages()) == FALSE) {install.packages("statnet")}
  if("igraph"   %in% rownames(installed.packages()) == FALSE) {install.packages("igraph")}
  if("gsheet"   %in% rownames(installed.packages()) == FALSE) {install.packages("gsheet")}
  

  library(statnet)
  library(igraph)
  library(gsheet)
  library(gdata)

#First let's load the data
  ##data in edgelist format
  relationships<-gsheet2tbl("https://docs.google.com/spreadsheets/d/1THL4Q4NO4XdFtF2Lgk3lpGuPOffLIp2Nk6y3XgvHnGs/edit?usp=sharing")
  relationships$To<-ifelse(relationships$To=="Unknown",ifelse(relationships$From=="Frey", "North", relationships$From),relationships$To)

  ##also import family and color information to match
  family<-gsheet2tbl("https://docs.google.com/spreadsheets/d/19w8dij4snBSREMpDoGzHXGC4K6Su0D8j2SY1rPYFSLQ/edit?usp=sharing")
  
##all marriages
  marriages<-relationships%>%
  filter(Type!="Affair")%>%
  group_by(From,To)%>%
  summarise(weight=n())

#Lets create a igraph object
      network_igraph<-graph_from_edgelist(as.matrix(marriages[,1:2]), directed=FALSE)
      E(network_igraph)$weight<-marriages$weight
      gotmarr.mat<-as.matrix(as_adj(network_igraph, attr="weight"))
      
      #igraph won't correct for strange edgelist with some asymmetry
      #export to statnet to fix and then reimport
      gotmarr.stat <- network(gotmarr.mat,ignore.eval=FALSE, names.eval="weight",directed = FALSE, loops=TRUE )
      gotmarr.stat%v%"color"<-family$Color[match(gotmarr.stat%v%"name", family$Family)]
      gotmarr.stat%v%"region"<-family$Region[match(gotmarr.stat%v%"name", family$Family)]
      gotmarr.mat<-as.matrix.network(gotmarr.stat,attrname = "weight")
      
      #reimport to igraph
      gotmarr.ig<-intergraph::asIgraph(gotmarr.stat)
      V(gotmarr.ig)$name<-V(gotmarr.ig)$vertex.names
      
      #all partners
      partners<-relationships%>%
        filter(Type!="Engaged")%>%
      group_by(From,To)%>%
        summarise(weight=n())
      
      #Lets create a igraph object
      network_igraph<-graph_from_edgelist(as.matrix(partners[,1:2]), directed=FALSE)
      E(network_igraph)$weight<-partners$weight
      gotpart.mat<-as.matrix(as_adj(network_igraph,attr="weight"))
      
      #igraph won't correct for strange edgelist with some asymmetry
      #export to statnet to fix and then reimport
      gotpart.stat <- network(gotpart.mat,ignore.eval=FALSE, names.eval="weight", directed = FALSE, loops=TRUE)
      gotpart.stat%v%"color"<-family$Color[match(gotpart.stat%v%"name", family$Family)]
      gotpart.stat%v%"region"<-family$Region[match(gotpart.stat%v%"name", family$Family)]
      gotpart.mat<-as.matrix.network(gotpart.stat,attrname = "weight")
  
      #reimport to igraph
      gotpart.ig<-intergraph::asIgraph(gotpart.stat)
      V(gotpart.ig)$name<-V(gotpart.ig)$vertex.names
      
  #Let's remove unessesary objects
  rm(family)
  rm(marriages)
  rm(network_igraph)
  rm(partners)
  
  gotmarr.nodes<-data.frame(name=gotmarr.stat%v%"vertex.names",
        degree=sna::degree(gotmarr.stat,gmode="graph"),
        degree.wt=strength(gotmarr.ig),
        bonpow=sna::bonpow(gotmarr.stat),
        betweenness=sna::betweenness(gotmarr.stat, gmode="graph"),
        close=sna::closeness(gotmarr.stat, gmode="graph"),
        constraint=constraint(gotmarr.ig))
```

# Inferential Stats

Looking at a 1,000 random networks, transitivity has a random chance to produce a value greater than the observed value, on all three factors (size, edges, dyads), especially when considering the number of nodes.



```{r}

cug.t<-function(cug.object){
  (cug.object$obs.stat-mean(cug.object$rep.stat))/sd(cug.object$rep.stat)
}

cugtransSize<-cug.test(gotmarr.mat,FUN=gtrans,mode="graph",cmode="size")
cugtransSize
cugtransEdges<-cug.test(gotmarr.mat,FUN=gtrans,mode="graph",cmode="edges")
cugtransEdges
cugtransDyad<-cug.test(gotmarr.mat,FUN=gtrans,mode="graph",cmode="dyad.census")
cugtransDyad

cug.t(cugtransSize)
cug.t(cugtransEdges)
cug.t(cugtransDyad)


par(mfrow=c(1,3))
plot(cugtransSize, main="Transitivity \nConditioned on Size" )
plot(cugtransEdges, main="Transitivity \nConditioned on Edges" )
plot(cugtransDyad, main="Transitivity \nConditioned on Dyads" )
par(mfrow=c(1,1))
```




Looking at a 1,000 random networks, betweenness has a random chance to produce a value greater than the observed value when compared to the properties edges and dyads. However, the property size was unable to generate a value higher than the observed betweenness score.


```{r}

cug.t<-function(cug.object){
  (cug.object$obs.stat-mean(cug.object$rep.stat))/sd(cug.object$rep.stat)
}

cugbetSize<-cug.test(gotmarr.mat,FUN=centralization, FUN.arg=list(FUN=betweenness, cmode="undirected"), mode="graph",cmode="size")
cugbetSize
cugbetEdges<-cug.test(gotmarr.mat,FUN=centralization, FUN.arg=list(FUN=betweenness, cmode="undirected"), mode="graph",cmode="edges")
cugbetEdges
cugbetDyad<-cug.test(gotmarr.mat,FUN=centralization, FUN.arg=list(FUN=betweenness, cmode="undirected"), mode="graph",cmode="dyad")
cugbetDyad

cug.t(cugbetSize)
cug.t(cugbetEdges)
cug.t(cugbetDyad)


par(mfrow=c(1,3))
plot(cugbetSize, main="Betweenness \nConditioned on Size" )
plot(cugbetEdges, main="Betweenness \nConditioned on Edges" )
plot(cugbetDyad, main="Betweenness \nConditioned on Dyads" )
par(mfrow=c(1,1))
```
